The Emotional Coherence Controversy: Evidence from Human and Automatic Expression Recognition

### 2019-04-22 ACII_2019_paper/ACII_2019_paper.Rmd
final

bibliography: mybibfile.bib
output: rticles::ieee_article
csl: http://www.zotero.org/styles/ieee
fig_caption: yes
keep_tex: yes
number_sections: yes
includes:
  in_header: preamble-latex.tex
---

>>>>

bibliography: mybibfile.bib
output: rticles::ieee_article
csl: http://www.zotero.org/styles/ieee
fig_caption: yes
keep_tex: yes
number_sections: yes
includes:
  in_header: preamble-latex.tex

template: C:/Users/dupred/Desktop/Projects/dynemo_feel_express/ACII_2019_paper/conference_041818.tex
---
